% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
%\documentclass[A4paper,11pt,orivec]{llncs}
\documentclass[orivec]{llncs}
%
\usepackage{color, colortbl}
\usepackage[inline]{enumitem}
\usepackage[table]{xcolor}
\usepackage{enumitem}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amsfonts,amsmath,amssymb,graphicx,setspace,times,tipx}
\usepackage[ruled,linesnumbered]{algorithm2e}
%\usepackage{subfig}
\usepackage{framed}
\usepackage{esvect}
\usepackage{tikz}
\usepackage{latexsym}
\usepackage{multirow}

%---------------------------

%\newtheorem*{mytheoii}{Theorem}
%-------------------------
\usepackage{array}
\usepackage{subcaption}
\captionsetup{compatibility=false}

\newcommand{\resizeT}{\scalebox{1}}
\newcommand{\resizeS}{\scalebox{.56}}
\newcommand{\resizeSS}{\scalebox{.38}}

\usepackage{longtable}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplots, pgfplotstable}

%\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
\usepackage{blkarray}% http://ctan.org/pkg/blkarra
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{adjustbox}
\usepackage{blindtext}
\usepackage{multicol}

\definecolor{bubblegum}{rgb}{0.99, 0.76, 0.8}




\usepackage{makecell, cellspace, caption}



\definecolor{Gray}{gray}{0.9}
%\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
%

\usepackage[first=0,last=9]{lcg}
\newcommand{\ra}{\rand0.\arabic{rand}}

\usepackage[title]{appendix}

\usepackage{boxedminipage}

\usepackage{multirow}


%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage[ruled,linesnumbered]{algorithm2e}
%\usepackage{enumitem}
%\usepackage[empty]{fullpage}% http://ctan.org/pkg/fullpage
%\usepackage{amsfonts,amsmath,amssymb,graphicx,setspace,times,tipx}
%\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
%\usepackage{blkarray}% http://ctan.org/pkg/blkarra


\usepackage{adjustbox}
\usepackage{blindtext}
\usepackage{multicol}
%\usepackage{lipsum}
%\usepackage{amsthm}
%\newtheorem*{assumption*}{\assumptionnumber}
\usepackage{tablefootnote}

\newtheorem{assumption}{Assumption}


\newcommand\NameEntry[1]{%
  \multirow{3}*{%
    \begin{varwidth}{10em}% --- or minipage, if you prefer a fixed width
    \flushright #1%
    \end{varwidth}}}




\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}


















\begin{document}
  \setlength\abovedisplayskip{0pt}
  \setlength\belowdisplayskip{0pt}


\newenvironment{packed_item}{
\begin{itemize}
	\setlength{\topsep}{0pt}
	\setlength{\partopsep}{0pt}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\newenvironment{packed_enum}{
\begin{enumerate}
	\setlength{\topsep}{0pt}
	\setlength{\partopsep}{0pt}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}




%\newtheorem{definition}{Definition}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{claim}{Claim}

\title{Multi-instance Publicly Verifiable Time-lock Puzzle\\ and its Applications}
%
%\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{}
%%
\institute{}

%\email{....}\\
%}

\maketitle              % typeset the title of the contribution
%
%\vspace{-6mm}


\begin{abstract}
Time-lock puzzles  are elegant  protocols that enable a party  to lock a message such that  no one else  can unlock it until a certain time  elapses. Nevertheless, existing  schemes are not suitable for the case where  a server is given \emph{multiple instances} of a puzzle scheme at once and  it  must unlock them at different points in time. If the schemes are naively used  in  this setting, then the server has to start solving all puzzles as soon as it receives them, that  ultimately imposes significant computation cost and demands a high  level of parallelisation. We put forth and formally define a primitive called ``\emph{multi-instance time-lock puzzle}'' which allows composing a puzzle's instances. We  propose a candidate construction: ``\emph{chained  time-lock puzzle}'' (C-TLP). It allows  the server, given instances' composition,  to solve  puzzles sequentially, without having to run parallel computations on them.  C-TLP makes black-box use of a standard time-lock puzzle scheme  and is  accompanied by a lightweight publicly verifiable algorithm. It is the first time-lock puzzle  that offers a combination of   the above features.  We utilise C-TLP  to build the first ``outsourced  proofs of retrievability''  that can support  \emph{real-time detection} and \emph{fair payment}  while having lower overhead than the state of the art.  
As another application of C-TLP,  we illustrate in certain cases, one can substitute a ``verifiable delay function''  with C-TLP, to gain much better efficiency. 
\end{abstract}


\input{Intro}
\input{related-work}
\input{Preliminary}
\input{multi-instance-TLP}
\input{PoR-Sec}
\input{Further-Applications-of-C-TLP}
\input{conclusion}


%\input{mod-2.tex}
% ---- Bibliography ----
%
%\bibliographystyle{splncs}

\bibliographystyle{splncs03}
\bibliography{main-ref}


\appendix
\input{Long-literature-review-appndx.tex}
\input{notation-Table.tex}
\input{R-TLP-Proof.tex}
\input{remarks.tex}
  \input{CR-TLP-proof}
 \input{CR-TLP-cost}
\input{PoR-definition.tex}
\input{SO-PoR-definition}
\input{SO-PoR-proof}
\input{SO-PoR-Extension}

\input{SO-PoR-Full-CostEvaluation.tex}
\input{PoSt-and-C-TLP}

%%%%%%%%%%%%%%%%%


\end{document}
